In the world of software development, the concept of microservices is gaining
popularity. This architectural style has received much attention in both
business and academia and converting a monolithic application into a
microservice-based application has become a regular practice. Companies
struggle with migrating their existing monolithic applications to
microservices, and software architects and developers frequently face
challenges due to a lack of complete awareness of alternative migration
methodologies, making the migration process even harder.

This dissertation aims to structurally analyse the state of the art in
migrating monolithic applications to microservices architectural style, mainly
which tools help architects, engineers, and developers and how automated they
are. A systematic literature review identified one hundred and six relevant
publications. These publications were organised and grouped to provide a more
comprehensive understanding of the current tools available for microservice
migration.

Furthermore, we present an extensible framework to help architects,
engineers, and developers during the migration process by addressing gaps in
understanding various migration tools and approaches, allowing for easy
comparison between multiple options. The application combines multiple tools
into one platform, allowing a comprehensive visualisation of migration
proposals and making it easy to compare different options. This application was
then subjected to an empirical study to extract usability and workload metrics
using System Usability Scale and Raw Task Load Index. The results proved
positive for usability and mixed for workload performance.
