In the world of software development, the concept of microservices is popular.
This architectural style has received much attention in both business and
academia, and converting a monolithic application into a microservice-based
application has become a regular practice. Companies struggle with migrating
their existing monolithic applications to microservices, and software
architects and developers frequently face challenges due to a lack of complete
awareness of alternative migration methodologies, making the migration process
even harder.

This dissertation aims to structurally analyse the state of the art in
migrating monolithic applications to microservices architectural style, mainly
which tools help architects, engineers, and developers and how automated they
are. A systematic literature review identified one hundred and six relevant
publications. These publications were organised and grouped to provide a more
comprehensive understanding of the current tools available for microservice
migration.

Furthermore, we present an extensible framework to help architects, engineers,
and developers during the migration process by addressing gaps in understanding
various migration tools and approaches, allowing for easy comparison between
multiple options. The application combines multiple tools into one platform,
allowing a comprehensive visualisation of migration proposals and making it
easy to compare different options.

To evaluate the efficacy of the application, we conducted an empirical study
that focused on assessing its usability and the associated workload experienced
by users during its utilisation. The study yielded favourable outcomes
concerning usability, indicating that participants found the application
user-friendly and intuitive. However, the workload results were diverse,
implying that the application's efficacy in mitigating overall workload during
the decomposition process was not universally experienced among the
participants.

\textbf{Keywords:} microservices, monoliths, decomposition, visualisation
