The query mentioned in the first iteration \Cref{subsub:first-iteration} was
then applied to DB.1, DB.2 and DB.3 and after applying the selection criteria
mentioned in \Cref{sub:selection-criteria}, results were gathered and
are presented in \Cref{tab:tool-search}.

\begin{table}[!htb] \caption{Tool Search} \label{tab:tool-search}
  \begin{center}
    \begin{tabular}[c]{p{5.5em}|p{5em}|p{5em}} \textbf{Database} &
      \textbf{Total\newline number\newline of results} &
      \textbf{Extracted\newline Results} \\
      \hline DB.1 & {118} & {3} \\
      \hline DB.2 & {4} & {0} \\
      \hline DB.3 & {658} & {3} \\
    \end{tabular}
  \end{center}
\end{table}

As for \href{https://github.com}{GitHub}, \href{https://gitlab.com}{GitLab} and
\href{https://duckduckgo.org}{DuckDuckGo}, the query would be essentially typed
into their respective search engine and the results gathered as well as the
query are presented in \Cref{tab:search-engine-tool-search}.

\begin{table}[!htb] \caption{Search Engine Tool Search}
  \label{tab:search-engine-tool-search}
  \begin{center}
    \begin{tabular}[c]{p{5.5em}|p{10em}|p{5em}|p{4em}}
      \textbf{Search\newline Engine} &
      \textbf{Query} &
      \textbf{Total\newline number\newline of results} &
      \textbf{Extracted\newline Results} \\
      \hline
        GitHub &
        \url{https://github.com/search?q=monolith+to+microservice} &
        {745} &
        {4} \\
      \hline
        GitLab &
        \url{https://gitlab.com/search?search=monolith\%20to\%20microservice} &
        {0} &
        {0} \\
      \hline
        DuckDuckGo &
        \url{https://duckduckgo.com/?q=monolith+to+microservices+tool} &
        {Uncountable} &
        {2} \\
    \end{tabular}
  \end{center}
\end{table}

Through this search process, we can also trace the references used in these
publications to determine if the tools described were based on previous work,
but only implemented a specific approach. This will help us to understand the
context and origins of these tools and how they fit into the broader landscape
of research in this area.

As for the second iteration mentioned in \Cref{subsub:second-iteration}, we
then proceeded to apply the query and search the first database. As shown in
\Cref{tab:db1-search}, from four hundred and fifty results, only twelve passed
the selection criteria defined in \Cref{sub:selection-criteria}.

\begin{table}[!htb] \caption{DB.1 Results} \label{tab:db1-search}
  \begin{center}
    \begin{tabular}[c]{p{5em}|p{5em}} \textbf{Total\newline number\newline of
      results} & \textbf{Extracted\newline New Results} \\
      \hline{450} & {12} \\
    \end{tabular}
  \end{center}
\end{table}

After reviewing the references of the identified papers and applying forward
and backward snowballing techniques, we were able to locate additional related
publications and expand the scope of our search as demonstrated in
\Cref{tab:db1-snowballing}. This helped us to increase the number of relevant
publications that we were able to consider in the next steps of the process.

\begin{table}[!htb] \caption{DB.1 Snowballing Results} \label{tab:db1-snowballing}
  \begin{center}
    \begin{tabular}[c]{p{8em}|p{8em}|p{8em}}
      \textbf{1st Forward} &
      \textbf{2nd Forward} &
      \textbf{Backward} \\
      \hline{23} &
      {2} &
      {45} \\
    \end{tabular}
  \end{center}
\end{table}

\begin{table}[!htb] \caption{Remaining DB Results} \label{tab:other-db-search}
  \begin{center}
    \begin{tabular}[c]{p{5em}|p{5em}|p{5em}}
      \textbf{Database} &
      \textbf{Total\newline number\newline of results} &
      \textbf{Extracted\newline New Results} \\
      \hline {DB.5 - 1st} & {21} & {1} \\
      \hline {DB.5 - 2nd} & {0} & {0} \\
      \hline {DB.4} & {9} & {3} \\
      \hline {DB.6} & {114} & {12} \\
      \hline {DB.3} & {20} & {0} \\
      \hline {DB.2} & {0} & {0} \\
    \end{tabular}
  \end{center}
\end{table}

In the case of Science Direct, as presented in \Cref{tab:other-db-search},
two queries were done. The main reason for this is that Science Direct is
limited to 7 \textit{OR} conditions, therefore it was necessary to split it
into two queries where it does not affect the general condition. In the
specific case, the \textit{``evolv"} keyword was moved into a separate query.
Also, Science Direct automatically accepts truncations without using the
\textit{``*"} char. The two queries are:

\begin{enumerate}
  \item \emph{(microservice OR "micro-service") AND ( migrat OR decompos OR
    identif OR refactor OR extract OR discover OR transition)}
  \item \emph{(microservice OR "micro-service") AND (evolv)}
\end{enumerate}

After iterating over the results and reviewing the references of the newly
found publications, we did not identify any additional publications that were
worth including in the final list. This marked the end of our general search
for relevant publications. We were able to find one hundred and six relevant
publications.
