To identify relevant publications for this research, we will utilise a range of
keywords related to the topic of microservices. These keywords will include
various phrases and terms used to describe microservices. As for the practices
that may help identification of microservices, keywords that help this
architectural refactoring should be included, such as ``migration'',
``refactor'', ``identification''. It could also be useful to use ``monolith'' (and
all its possible synonyms) to be the comparison against ``microservices'',
although this can result in some extra publications not related to
microservices but instead related to ``service-oriented architecture''. An
expected outcome or conclusion of the publication could be included,
``approach'' or even ``tool''. The main keywords that will be used are present in
\Cref{tab:keywords}.

\begin{table}[!htb] \caption{Keywords} \label{tab:keywords}
  \begin{center}
    \begin{tabular}[c]{p{7em}|p{13em}} {\textbf{Focus}} & microservices \\
      \hline \textbf{Refactoring} & {migration, decomposition, identify, refactor, evolve, discover, transition } \\
      \hline \textbf{Target} & monolith \\
      \hline \textbf{Outcome} & approach, tool \\
    \end{tabular}
  \end{center}
\end{table}

Initially the focus was in determining how many tools exist that are able to
solve this research question or, at the very least, help partially with it. In
order to do this, one could not be limited to tools that are documented in
academic databases therefore, in addition to the databases mentioned in
\Cref{tab:databases}, \href{https://github.com}{GitHub},
\href{https://gitlab.com}{GitLab} and even
\href{https://duckduckgo.org}{DuckDuckGo} were searched for, even though they
do not represent a scientific search engine.

By using some keywords mentioned in \Cref{tab:keywords} the following
initial trial query was created:

\begin{center}
  \emph{(``microservice'' OR ``micro-service'') AND (``migration'' OR
  ``identification'') AND (``monolithic'' OR ``monolith'') AND (``tool'')}
\end{center}

Afterwards, the focus was on locating publications that describe alternative
approaches for migrating from monolithic to microservices architectures that
may not have been implemented in practice. This will allow an increased
understanding of the current state of the art in this area, identify any gaps
or areas where further research is needed, and determine what can be improved
upon. This information will be useful in guiding the development of our tool
and abstraction.

Relying on the keywords identified in \Cref{tab:keywords}, the following
query was created:

\begin{center}
  \emph{(microservice* OR micro?service*) AND (migrat* OR identif*) AND
  (monolith*) AND (migrat* NEAR/2 (process* OR approach*))}
\end{center}

In the event that the publications located through the snowballing approach are
no longer adding significant value to the overall understanding of the topic, a
new search query should be applied to the remaining databases. In some
instances, the query produced more than two thousand results, which would have
been impractical to analyse within the given timeframe. Therefore, we modified
the query to focus only on the titles and abstracts of the publications. The
revised query that should be used is:

\begin{center}
  \emph{(microservice* OR ``micro-service'') AND (migrat* OR decompos* OR
  identif* OR refactor* OR evolv* OR extract* OR discover* OR transition*)}
\end{center}
