TypeScript, an open-source language developed and maintained by Microsoft
\cite{typescript-announcement}, is considered a superset of JavaScript that
introduces static typing to the language \cite{typescript-explanation}. The
motivation behind TypeScript originates from the shortcomings experienced when
developing large-scale applications with JavaScript. While JavaScript offers
speed and ease of use, as projects grow in size and complexity, maintaining and
updating it becomes increasingly challenging.

TypeScript brings some benefits, namely:

\begin{itemize}
  \item Compilation: TypeScript code must be compiled to JavaScript before
    execution. This compilation step allows developers to identify errors
    during the process. If there is an invalid code, the compilation will
    fail, providing an opportunity to catch and rectify errors before
    runtime.

  \item Strong and Static Typing: TypeScript introduces a type system that
    builds upon JavaScript. While JavaScript permits variables to have any
    type, TypeScript enforces static typing, requiring developers to
    explicitly declare the type of variables, functions, methods, and many
    more. This approach promotes code clarity and helps prevent type-related
    errors by ensuring that variables are assigned appropriate types and used
    correctly throughout the codebase.

\end{itemize}

For this work, TypeScript is used transversally across all implementations.
Anytime JavaScript is required, TypeScript is used instead.
