Given that software development is never finished, there are two areas for
future improvements: enhancements to the application and refinements in the
evaluation process.

In terms of application improvements, valuable insights were obtained through
the feedback questionnaire (depicted in \Cref{fig:questionaire_feedback}),
leading to the identification of several potential future enhancements:

\begin{itemize}
  \item \textbf{Enhancing metadata descriptions for improved comparisons:} The
    application only presents metadata metrics without accompanying
    explanations for each metadata. It would be beneficial to provide
    descriptions for metadata attributes to facilitate better understanding and
    comparisons. One participant stated \textit{``Add explanation for terms
    like Modularity and Resolution''}, while other \textit{`` The modularity
    and resolution could be explained a bit further''}.

  \item \textbf{Implementing decomposition tracking features:} Introducing
    functionality to track decompositions would enable users to manage and
    differentiate between various decompositions, like selecting favourites or
    marking decompositions as already viewed. Such features assist users in
    discarding irrelevant decompositions while retaining others for future
    comparisons. As suggested by one participant \textit{``When selecting
      decomposition results for comparison, having an option to mark each
    decomposition result as viewed or analyzed would help the use''}, and
    another stated \textit{``Save decomposition id, like a favorites menu''}.

  \item \textbf{Establishing bidirectional relationships between microservices
    and modules:} When focusing on a specific microservice, the application
    displays the list of modules that compose it. However, this relationship is
    unidirectional. It would be advantageous to establish a two-way
    association, enabling users to select a module and visualise all the
    corresponding microservices across different decompositions. The suggestion
    is \textit{``Have a list of classes and when selected show in the graph in
      which service it belongs to (even when comparing multiple
    decompositions)''}

  \item \textbf{Incorporating refactoring tools:} Providing a preview step for
    tools before the refactoring. At the moment, there are some tools that
    already do code refactor \citeSLR{freitas2021refactoring}, but do not
    provide a way of previewing it. It could be benefitial to ``inject'' this
    solution in the middle of the process, going from decomposition, into
    visualisation, into refactoring.
\end{itemize}

In terms of evaluation improvements, some considerations should be taken into
account for future studies, specifically:

\begin{itemize}
  \item \textbf{Expanding the respondent pool:} Increasing the number of
    participants in evaluations can enhance the reliability and
    generalizability of the findings. A more extensive and diverse group of
    respondents can capture a more comprehensive range of perspectives and
    experiences, leading to more robust conclusions.
  \item \textbf{Incorporating a comparative approach:} Participants should be
    engaged in both tasks, one without utilising the application and only using
    the underlying tools and another while using the application. By comparing
    the outcomes and experiences between these two scenarios, the added value
    and impact of the application can be assessed more accurately.
    Additionally, employing different tasks with similar-sized projects can
    help evaluate the application's performance across various contexts and
    validate its usefulness in different scenarios.
  \item \textbf{Broadening the task pool and project size range:} Diversifying
    the available tasks and expanding the range of project sizes used in
    evaluations contribute to a more comprehensive assessment of the
    application.
\end{itemize}
